Cross frequency coupling of attentional EEG task under pain

### 2020-08-28 ManuscriptMarkdown.Rmd
Adjusted code to investigate illogical RT

```{r Packages and Libraries, message = FALSE, warning = FALSE, echo = FALSE}
# installs packages if necessary - MUST locate packages before knitting
.libPaths("./Packages")
Packages <- c("ggplot2","dplyr","reshape","wesanderson",
              "BayesFactor",
              "kableExtra","rmatio","Rmisc",
              "rmarkdown","data.table","devtools",
              "cowplot","dplyr","readr") # Slew of packages used here.

@@

@@

# 2. Methods
```{r Methods Set-up, echo=FALSE}
# As per the following document. Only CLP106 -> CLP 149 are useable
PainCodes <- read.csv("EEGIdentity.csv")
PainCodes$Subjidx <- paste("CLP",PainCodes$Subjidx,sep = "")

Subjidx <- dir(path = "Data/RejectData/",
               pattern = "CLP*")
# Remove CLP116_2 until we know what that's about.
Subjidx <- Subjidx[Subjidx != "CLP116_2"]

# Seperate into those with pain data and those without
pain_Subjidx <- Subjidx[unlist(
  lapply(Subjidx, function(px)
    file.exists(
      paste("Data/RejectData/", px, "/", px, "_p_BadChannels.txt",sep = "")
    )))]

# Reduce particpants down to finalised numbers
PainCodes <- PainCodes[PainCodes$Subjidx %in% Subjidx,]

@@

## Below code only runs the first time. If Output/Trial_list exsits it will simply load the data.
if(!file.exists("Output/Trial_list.RData")){
Trial.list <- list()
## Extract Trial.list
for(px in seq_along(Subjidx)){
  Trial.list[["np"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],COND = "np")

}
names(Trial.list[["np"]]) <- Subjidx

# N.B - CLP116 is missing pain data
Subjidx_p <- Subjidx[-16]
for (px in seq_along(Subjidx)) {
  if (file.exists(paste(
    "../Data/",
    Subjidx[px],
    "/Behaviour/",
    paste(Subjidx[px], "p", sep = "_"),
    "_EventCodes.mat",
    sep = ""
  ))) {
    Trial.list[["p"]][[px]] <-
      ExtractTrialData(PartID = Subjidx[px], COND = "p")
  }
  else {
    Trial.list[["p"]][[px]] <- NA
  }
}
names(Trial.list[["p"]]) <- Subjidx

## Remove CLP116 pain data
Trial.list[["p"]][is.na(Trial.list[["p"]])] <- NULL

save(Trial.list,file = "Output/Trial_list.RData")

Trialdata <- rbind(data.table::rbindlist(Trial.list$np),
                 data.table::rbindlist(Trial.list$p))
write.csv(Trialdata,file = "Output/TrialData.csv",
          row.names = F)
}

## Load data
tmp = load("Output/Trial_list.RData")
Trialdata <- read.csv("Output/TrialData.csv")
Trialdata <- Trialdata[Trialdata$PartID %in% Subjidx,]

## check CTI and ITI values:
hist(Trialdata$CTI)
hist(Trialdata$ITI)
table(Trialdata$PartID[Trialdata$ITI>4000]) # CLP114 and CLP124 might need a look into for long ITIs

## Calculate summary variables and store in data frame
source('Functions/MethodsList.R')
Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: mean RT for miss trials/SD for 2 trials total
```

@@

  Cues were displayed for 250ms and targets for 60ms [*Please confirm this is correct. Trigger codes did not specify exactly*]. The cue to target interval (CIT) jittered between `r round(min(Trialdata$CTI,na.rm=T),0)`-`r round(max(Trialdata$CTI,na.rm=T),0)` in steps of **XXX** (*Values for this change with participants. Some have maxes of ~800ms and min of ~700ms. Others (N = 3) have max ~1500 and min ~1400* **I beleive I have fixed this with removal of some px**). Each trial lasted approximately `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`, with a jitter of **XXX**.

@@

@@

## Collate number of removed channels
EEGPreProc[["BadChan"]][["np"]] <- lapply(Subjidx,
                                          function(px)
                                            nrow(
                                              read.table(
                                                paste("Data/RejectData/",
                                                      px, "/",
                                                      px,
                                                      "_np_BadChannels.txt",
                                                      sep = ""),
                                                row.names = NULL,
                                                quote = "\"",
                                                comment.char = ""
                                              )
                                            ))

@@

EEGPreProc[["BadChan"]][["p"]] <- lapply(pain_Subjidx,
                                         function(px)
                                           nrow(
                                             read.table(
                                               paste("Data/RejectData/",
                                                     px, "/",
                                                     px,
                                                     "_p_BadChannels.txt",
                                                     sep = ""),
                                               row.names = NULL,
                                               quote = "\"",
                                               comment.char = ""
                                             )
                                           ))

names(EEGPreProc[["BadChan"]][["p"]]) <- pain_Subjidx

@@

## Summarise number of removed components
EEGPreProc[["RejComp"]][["np"]] <- lapply(Subjidx,
                                          function(px)
                                            nrow(
                                              read.table(
                                                paste("Data/RejectData/",
                                                      px, "/",
                                                      px,
                                                      "_np_RejectedComps.txt",
                                                      sep = ""),
                                                row.names = NULL,
                                                quote = "\"",
                                                comment.char = ""
                                              )
                                            ))

@@

EEGPreProc[["RejComp"]][["p"]] <- lapply(pain_Subjidx,
                                         function(px)
                                           nrow(
                                             read.table(
                                               paste("Data/RejectData/",
                                                     px, "/",
                                                     px,
                                                     "_p_RejectedComps.txt",
                                                     sep = ""),
                                               row.names = NULL,
                                               quote = "\"",
                                               comment.char = ""
                                             )
                                           ))

names(EEGPreProc[["RejComp"]][["p"]]) <- pain_Subjidx

@@

## Summarise number of removed trials
EEGPreProc[["RejTrial"]][["np"]][["Visual"]] <- lapply(Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_np_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[1, 1]])

names(EEGPreProc[["RejTrial"]][["np"]][["Visual"]]) <- Subjidx

EEGPreProc[["RejTrial"]][["np"]][["Auditory"]] <- lapply(Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_np_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[2, 1]])

names(EEGPreProc[["RejTrial"]][["np"]][["Auditory"]]) <- Subjidx

EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]] <- lapply(Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_np_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[3, 1]])

names(EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]]) <- Subjidx

EEGPreProc[["RejTrial"]][["p"]][["Visual"]] <- lapply(pain_Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_p_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[1, 1]])

names(EEGPreProc[["RejTrial"]][["p"]][["Visual"]]) <- pain_Subjidx

EEGPreProc[["RejTrial"]][["p"]][["Auditory"]] <- lapply(pain_Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_p_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[2, 1]])

names(EEGPreProc[["RejTrial"]][["p"]][["Auditory"]]) <- pain_Subjidx

EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]] <- lapply(pain_Subjidx,
                                                       function(px)
                                                         read.table(
                                                           paste(
                                                             "Data/RejectData/",
                                                             px,
                                                             "/",
                                                             px,
                                                             "_p_RF_Proc_RejTrials.txt",
                                                             sep = ""
                                                           ),
                                                           row.names = NULL,
                                                           quote = "\"",
                                                           comment.char = ""
                                                         )[[3, 1]])

names(EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]]) <- pain_Subjidx

# Both conditions together
EEGPreProc[["RejTrial"]][["Both"]][["Visual"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Visual"]][Subjidx],                                                       EEGPreProc[["RejTrial"]][["p"]][["Visual"]][Subjidx]), Subjidx)

EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Auditory"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Auditory"]][Subjidx]), Subjidx)

EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]][Subjidx]), Subjidx)

# Both conditions averaged
EEGPreProc[["RejTrial"]][["Average"]][["Visual"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Visual"]][[x]]))

EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]][[x]]))

EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]][[x]]))

## Total Trials Removed
EEGPreProc[["RejTrial"]][["Total"]] <- lapply(seq_along(Subjidx),
                                              function(x)
                                              sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[x]],
                                              EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[x]],
                                              EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[x]]))

Perc_TrialsRemoved <- data.frame(Vis = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]])/120),
                            Aud = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]])/120),
                            Amb = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]])/60))
## Compare Cue Types on the percentage of removed trials
# format data
TrialsRemoved_test <- reshape2::melt(Perc_TrialsRemoved)
# Freq test
TR_ANOVA <- aov(value ~ variable, data = TrialsRemoved_test)
# Bayes test
BF_TR_ANOVA <- BayesFactor::anovaBF(value ~ variable, data = TrialsRemoved_test)

@@

  An outline of the EEG pre-processing undertaken here is presented in Figure *X*. EEG data were first average referenced and high pass filtered at 1Hz using the *removeTrend* function. Line noise of 6Hz and its associated harmonics was removed using a notch filter before the *clean_artifacts* function was used to detect bad channels. Channels were marked for removal is there was noise greater than 4 standard deviations greater than the mean, 1/5th of the channel was flat, or correlations with other channels was lower than .8. This processed removed an average of `r round(mean(unlist(EEGPreProc$BadChan$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$BadChan$Average)),2)` of channels. The results of this were visually inspected ad confirmed before data was subjected to ICA. Resulting components from the *run_ica* output was marked for removal with the the ICLabel algorthm, where compnents classifed greater than 75% eye, greater than 80% muscle, or greater than 90% heart, line, and channel were removed. Visual inspection confirmed the component removal and the ICA weights were saved for later referral.
  The final EEG data set was high pass filtered at 0.1Hz. Bad channels were removed and ICA weights were added to the data and bad components removed. An average of `r round(mean(unlist(EEGPreProc$RejComp$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejComp$Average)),2)` copmonents were removed for each participant. Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately. EEGLABs extreme epoch noise detection using EEGLab's threshold & joint probability procedures was undertaken with the cut-off for amplitude set at 100uV **put in other stuff heree**. An average of `r round(mean(unlist(EEGPreProc$RejTrial$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejTrial$Average)),2)` trials were removed using this procedure for each participant. Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.
  An average of `r round(mean(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` +/- `r round(sd(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` trials were removed for each participant. There was no influence of Cue Type on the percentage of trials removed, as shown with a one-way ANOVA (`r papaja::apa_print.aov(TR_ANOVA)$full_result$variable`). An equivilant Bayesian ANOVA showed evidence for the null (BF~10~ = `r round(extractBF(BF_TR_ANOVA)[[1]],3)`).
  Time freqeucny transform was undertaken closely following the advice of Cohen (2014; *check refrence*). In short, Morelt wavelets were created at different frequency dependent widths. Across the 80 linearlly spaced frequency bins between 3 and 30Hz, wavelets were created with widths between 6 and 10 cycles. In other words, smaller width wavelets were used for slower frequencies and larger width wavelets were used for faster frequncies. This allowed for the investigation of multiple freqency bands (i.e., both Theta and Alpha) with approximately the same resolution. The output of this process was baselined using a decibel conversion to the time period -500 to -200ms pre-cue. ERPs to each cue were taken for the time period up to 1 second post cue. To control for high frequency noise, the data were low pass filtered at 30Hz for the ERP analyis. ERPs were baselined -200ms to cue onset (i.e., 0ms).

@@

# Create list and loop through plots
if(!file.exists("Output/RT_Rainplots.RData")){
Plots <- list()
RT_comp_xvals <- c("Target","CueType","Distractor","Condition")
RT_comp_groupvals <- c("Accuracy","Target","CueType","Distractor","Condition")

for (i in seq_along(RT_comp_xvals)){
Plots[[RT_comp_xvals[i]]] <- lapply(RT_comp_groupvals,function(x) RT_RainPlot(data = Trialdata,
                                                                      xval = RT_comp_xvals[i],
                                                                      groupval = x))
names(Plots[[RT_comp_xvals[i]]]) <- RT_comp_groupvals
}
save(Plots,file = "Output/RT_Rainplots.RData")

@@

## Plot Errors and Omissions Data
# Create list and loop through plots
source('Functions/Error_RainPlots.R')
if(!file.exists("Output/Errors_Rainplots.RData")){
Error_comp_xvals <- "Accuracy"
Error_comp_groupvals <- c("Target","CueType","Distractor","Condition")

>>>>

```{r Packages and Libraries, message = FALSE, warning = FALSE, echo = FALSE}
# installs packages if necessary - MUST locate packages before knitting
.libPaths("./Packages")
Packages <- c("ggplot2","dplyr","reshape","wesanderson",
              "BayesFactor",
              "kableExtra","rmatio","Rmisc",
              "rmarkdown","data.table","devtools",
              "cowplot","readr") # Slew of packages used here.

@@

# Seed setting for Bayes
set.seed(930129)

@@

# 2. Methods
```{r Methods Set-up, echo=FALSE}
# As per the following document. Only CLP106 -> CLP 149 are useable
PainCodes <- read.csv("PainRatings.csv")
PainCodes$Subjidx <- paste("CLP",PainCodes$Subjidx,sep = "")

Subjidx <- dir(path = "Data/",
               pattern = "CLP*")

# Remove CLP116 - Didn't finish
Subjidx <- Subjidx[Subjidx != "CLP116"]
# Remove CLP1107 - Odd Trigger codes 
Subjidx <- Subjidx[Subjidx != "CLP107"]
# Remove CLP130 - Odd trigger codes
Subjidx <- Subjidx[Subjidx != "CLP130"]

@@

## Below code only runs the first time. If Output/Trial_list exsits it will simply load the data.
if(!file.exists("Output/Trial_list.RData")){
Trial.list <- list(np = list(),
                   p = list())
## Extract Trial.list
for(px in seq_along(Subjidx)){
  Trial.list[["np"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],
                                               COND = "np",
                                               dataloc = "Data/")

}
names(Trial.list[["np"]]) <- Subjidx
Trial.list[["np"]] <- Trial.list[["np"]][!is.na(Trial.list[["np"]])]

for(px in seq_along(Subjidx)){
  Trial.list[["p"]][[px]] <- ExtractTrialData(PartID = Subjidx[px],
                                               COND = "p",
                                               dataloc = "Data/")

}
names(Trial.list[["p"]]) <- Subjidx
Trial.list[["p"]] <- Trial.list[["p"]][!is.na(Trial.list[["p"]])]

save(Trial.list, file = "Output/Trial_list.RData")
Trialdata <- rbind(data.table::rbindlist(Trial.list[["np"]]),
                   data.table::rbindlist(Trial.list[["p"]]))

# Mark participants who recieved pain:
Trialdata$Rec_pain <- 0
Trialdata$Rec_pain[Trialdata$PartID %in% PainCodes$Subjidx] <- 1

write.csv(Trialdata, file = "Output/TrialData.csv",
          row.names = F)
}

## Load data
tmp = load("Output/Trial_list.RData")
Trialdata <- read.csv("Output/TrialData.csv")

# Subset Participants from Trialdata
Trialdata <- Trialdata[Trialdata$PartID %in% Subjidx,]
Trialdata$PartID <- factor(Trialdata$PartID)
rownames(Trialdata) <- seq(from = 1, to = nrow(Trialdata),by=1)
```

``` {r Sanity Checks}

#### TODO Fix this section up. Make it presentable ####
### We want to:
# Find incorrect trigger codes, i.e., short/long CTI/ITIs and remove
# Cut short RT ~<150ms
# Cut long RT >1000ms?

hist(Trialdata$RT, breaks = 100)
hist(Trialdata$RT[Trialdata$RT<250], breaks = 100)

table(Trialdata$PartID[Trialdata$RT<150])
table(Trialdata$Condition[Trialdata$RT<150]) # Slight condition difference
table(Trialdata$Accuracy[Trialdata$RT<150])

# Long responses
table(Trialdata$PartID[Trialdata$RT>800])
table(Trialdata$Condition[Trialdata$RT>800])
table(Trialdata$Accuracy[Trialdata$RT>800])

## check CTI and ITI values:
hist(Trialdata$CTI, breaks = 100)
hist(Trialdata$CTI[Trialdata$CTI<700], breaks = 100)
table(Trialdata$PartID[Trialdata$CTI<600]) # One short CIT. - Error
ShortCTI <- list(,
                 )

# Remove it
Trialdata <- Trialdata[-c(10271,12882),]

hist(Trialdata$CTI[Trialdata$CTI>800], breaks = 100)
table(Trialdata$PartID[Trialdata$CTI>850]) # One long CTI - Miss

median(Trialdata$CTI, na.rm = T)
min(Trialdata$CTI[Trialdata$CTI>500], na.rm = T)

hist(Trialdata$ITI, breaks = 100)
table(Trialdata$ITI)
hist(Trialdata$ITI[Trialdata$ITI>2500], breaks = 100)
hist(Trialdata$ITI[Trialdata$ITI<2000], breaks = 100)

table(Trialdata$PartID[Trialdata$ITI>3000])
table(Trialdata$PartID[Trialdata$ITI<1850])

Trialdata <- Trialdata[-c(4823),]

summary(Trialdata$ITI[Trialdata$ITI<3000])

Trialdata$RT[Trialdata$RT<150] <- NA

## Re-level the CueType data into cued and ambiguous
levels(Trialdata$CueType) <- list("Ambiguous" = "Ambiguous", "Cued" = c("Auditory","Visual"))

## Plot pain response
painplots <- PainCodes %>% dplyr::filter(AveragePainRating >= 20) %>% dplyr::select(Subjidx,Start,contains("Break")) %>% 
  tidyr::gather(Time,Pain,Start:Break5)
painplots$Time <- factor(painplots$Time,levels = c("Start", "Break1", "Break2", "Break3", "Break4", "Break5"))

painplots_summ <- Rmisc::summarySEwithin(
  painplots,
  measurevar = "Pain",
  withinvars = "Time",
  idvar = "Subjidx",
  na.rm = T,
  conf.interval = .95
)

ggplot(data = painplots,aes(x = Time,y = Pain,group = Subjidx,colour = Subjidx)) +
  geom_point() + geom_line() +
    stat_summary(aes(y = Pain,group=1), fun=mean, colour="red", lwd = 1, geom="line",group=1) +
      # stat_summary(aes(y = Pain,group=1),fun.data = mean_se,colour="red", lwd = 1,
      #            geom = "errorbar")+
  theme_classic() +
  theme(legend.position = 'none') +
  labs(x = "Time Points",
       y = "Pain Rating (%)") + 
    scale_colour_grey()

## Calculate summary variables and store in data frame
source('Functions/MethodsList.R')
Summdata <- MethodsList(Trialdata) # Can ignore warnings - RE: mean RT for miss trials/SD for 2 trials total
# Mark participants who recieved pain:
Summdata$Rec_pain <- 0
Summdata$Rec_pain[Summdata$PartID %in% PainCodes$Subjidx] <- 1
```

@@

  Cues were displayed for 250ms and targets for 60ms [*Please confirm this is correct. Trigger codes did not specify exactly*]. The cue to target interval (CIT) jittered between `r min(Trialdata$CTI[Trialdata$CTI>300],na.rm = T)`-`r max(Trialdata$CTI[Trialdata$CTI<1400],na.rm = T)` in steps of **XXX** (*Values for this change with participants. Some have maxes of ~800ms and min of ~700ms. Others have max ~1500 and min ~200*). Each trial lasted an average of `r round(mean(Trialdata %>% group_by(PartID) %>% summarise(meanITI = mean(ITI,na.rm=T)) %>% .$meanITI),0)`ms.

@@

### 2.2.3. Heat Pain
  Pain was delivered

@@

## Collate number of removed channels
EEGPreProc[["BadChan"]][["np"]] <- lapply(Subjidx,
                                          function(px)
                                            nrow(
                                              read.table(
                                                paste("Data/",
                                                      px, "/Stats/",
                                                      px,
                                                      "_np_BadChannels.txt",
                                                      sep = ""),
                                                row.names = NULL,
                                                quote = "\"",
                                                comment.char = ""
                                              )
                                            ))

@@

EEGPreProc[["BadChan"]][["p"]] <- lapply(Subjidx,
                                         function(px)
                                           nrow(
                                             read.table(
                                               paste("Data/",
                                                      px, "/Stats/",
                                                      px,
                                                      "_p_BadChannels.txt",
                                                      sep = ""),
                                               row.names = NULL,
                                               quote = "\"",
                                               comment.char = ""
                                             )
                                           ))

names(EEGPreProc[["BadChan"]][["p"]]) <- Subjidx

@@

## Summarise number of removed components
EEGPreProc[["RejComp"]][["np"]] <- lapply(Subjidx,
                                          function(px)
                                            nrow(
                                              read.table(
                                                paste("Data/",
                                                      px, "/Stats/",
                                                      px,
                                                      "_np_RejectedComps.txt",
                                                      sep = ""),
                                                row.names = NULL,
                                                quote = "\"",
                                                comment.char = ""
                                              )
                                            ))

@@

EEGPreProc[["RejComp"]][["p"]] <- lapply(Subjidx,
                                         function(px)
                                           nrow(
                                             read.table(
                                                paste("Data/",
                                                      px, "/Stats/",
                                                      px,
                                                      "_p_RejectedComps.txt",
                                                      sep = ""),
                                               row.names = NULL,
                                               quote = "\"",
                                               comment.char = ""
                                             )
                                           ))

names(EEGPreProc[["RejComp"]][["p"]]) <- Subjidx

@@

## Summarise number of removed trials - Removed from current pipeline
# EEGPreProc[["RejTrial"]][["np"]][["Visual"]] <- lapply(Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_np_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[1, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["np"]][["Visual"]]) <- Subjidx
# 
# EEGPreProc[["RejTrial"]][["np"]][["Auditory"]] <- lapply(Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_np_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[2, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["np"]][["Auditory"]]) <- Subjidx
# 
# EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]] <- lapply(Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_np_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[3, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]]) <- Subjidx
# 
# 
# EEGPreProc[["RejTrial"]][["p"]][["Visual"]] <- lapply(pain_Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_p_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[1, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["p"]][["Visual"]]) <- pain_Subjidx
# 
# EEGPreProc[["RejTrial"]][["p"]][["Auditory"]] <- lapply(pain_Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_p_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[2, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["p"]][["Auditory"]]) <- pain_Subjidx
# 
# EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]] <- lapply(pain_Subjidx,
#                                                        function(px)
#                                                          read.table(
#                                                            paste(
#                                                              "Data/RejectData/",
#                                                              px,
#                                                              "/",
#                                                              px,
#                                                              "_p_RF_Proc_RejTrials.txt",
#                                                              sep = ""
#                                                            ),
#                                                            row.names = NULL,
#                                                            quote = "\"",
#                                                            comment.char = ""
#                                                          )[[3, 1]])
# 
# names(EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]]) <- pain_Subjidx
# 
# # Both conditions together
# EEGPreProc[["RejTrial"]][["Both"]][["Visual"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Visual"]][Subjidx],                                                       EEGPreProc[["RejTrial"]][["p"]][["Visual"]][Subjidx]), Subjidx)
# 
# EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Auditory"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Auditory"]][Subjidx]), Subjidx)
# 
# EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]] <- setNames(mapply(c, EEGPreProc[["RejTrial"]][["np"]][["Ambiguous"]][Subjidx], EEGPreProc[["RejTrial"]][["p"]][["Ambiguous"]][Subjidx]), Subjidx)
# 
# # Both conditions averaged
# EEGPreProc[["RejTrial"]][["Average"]][["Visual"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Visual"]][[x]]))
# 
# EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Auditory"]][[x]]))
# 
# EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]] <- lapply(Subjidx,function(x) mean(EEGPreProc[["RejTrial"]][["Both"]][["Ambiguous"]][[x]]))
# 
# ## Total Trials Removed
# EEGPreProc[["RejTrial"]][["Total"]] <- lapply(seq_along(Subjidx),
#                                               function(x)
#                                               sum(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]][[x]],
#                                               EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]][[x]],
#                                               EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]][[x]]))
# 
# Perc_TrialsRemoved <- data.frame(Vis = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Visual"]])/120),
#                             Aud = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Auditory"]])/120),
#                             Amb = (unlist(EEGPreProc[["RejTrial"]][["Average"]][["Ambiguous"]])/60))
# ## Compare Cue Types on the percentage of removed trials
# # format data
# TrialsRemoved_test <- reshape2::melt(Perc_TrialsRemoved)
# # Freq test
# TR_ANOVA <- aov(value ~ variable, data = TrialsRemoved_test)
# # Bayes test
# BF_TR_ANOVA <- BayesFactor::anovaBF(value ~ variable, data = TrialsRemoved_test)

@@

  An outline of the EEG pre-processing undertaken here is presented in Figure *X*. EEG data were first average referenced and high pass filtered at 1Hz using the *removeTrend* function. Line noise of 6Hz and its associated harmonics was removed using a notch filter before the *clean_artifacts* function was used to detect bad channels. Channels were marked for removal is there was noise greater than 4 standard deviations greater than the mean, 1/5th of the channel was flat, or correlations with other channels was lower than .8. This processed removed an average of `r round(mean(unlist(EEGPreProc$BadChan$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$BadChan$Average)),2)` of channels. The results of this were visually inspected ad confirmed before data was subjected to ICA. Resulting components from the *run_ica* output was marked for removal with the the ICLabel algorthm, where compnents classifed greater than 75% eye, greater than 80% muscle, or greater than 90% heart, line, and channel were removed. Visual inspection confirmed the component removal and the ICA weights were saved for later referral.
  The final EEG data set was high pass filtered at 0.1Hz. Bad channels were removed and ICA weights were added to the data and bad components removed. An average of `r round(mean(unlist(EEGPreProc$RejComp$Average)),2)` +/- `r round(sd(unlist(EEGPreProc$RejComp$Average)),2)` copmonents were removed for each participant. Channels were then interpolated using *pop_interp* and data epoched 1.5s before the cue to 2.5s post-cue, for each cue seperately. Lastly, data were current source density transformed useing Fieldtrips *ft_scalpcurrentdensity* using the spline method.
  <!-- An average of `r round(mean(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` +/- `r round(sd(unlist(EEGPreProc[["RejTrial"]][["Total"]])),2)` trials were removed for each participant. There was no influence of Cue Type on the percentage of trials removed, as shown with a one-way ANOVA (`r papaja::apa_print.aov(TR_ANOVA)$full_result$variable`). An equivilant Bayesian ANOVA showed evidence for the null (BF~10~ = `r round(extractBF(BF_TR_ANOVA)[[1]],3)`). -->
  Time freqeucny transform was undertaken closely following the advice of Cohen (2014; *check refrence*). In short, Morelt wavelets were created at different frequency dependent widths. Across the 80 linearlly spaced frequency bins between 3 and 30Hz, wavelets were created with widths between 6 and 10 cycles. In other words, smaller width wavelets were used for slower frequencies and larger width wavelets were used for faster frequncies. This allowed for the investigation of multiple freqency bands (i.e., both Theta and Alpha) with approximately the same resolution. The output of this process was baselined using a decibel conversion to the time period -500 to -200ms pre-cue. ERPs to each cue were taken for the time period up to 1 second post cue. To control for high frequency noise, the data were low pass filtered at 30Hz for the ERP analyis. ERPs were baselined -200ms to cue onset (i.e., 0ms).

@@

# Create list and loop through plots
if(!file.exists("Output/RT_Rainplots.RData")){
Plots <- list()
RT_comp_xvals <- c("Target","CueType","Distractor")
RT_comp_groupvals <- c("Accuracy","Target","CueType","Distractor")

for (i in seq_along(RT_comp_xvals)){
Plots[[RT_comp_xvals[i]]] <- lapply(RT_comp_groupvals,function(x) RT_RainPlot(data = Trialdata,
                                                                      xval = RT_comp_xvals[i],
                                                                      groupval = x))
names(Plots[[RT_comp_xvals[i]]]) <- RT_comp_groupvals
}

Plots[[RT_comp_xvals[i]]] <- lapply(RT_comp_groupvals,function(x) RT_RainPlot(data = Trialdata[Trialdata$Rec_pain==1,],
                                                                      xval = "Condition",
                                                                      groupval = x))
names(Plots[[RT_comp_xvals[i]]]) <- RT_comp_groupvals

save(Plots,file = "Output/RT_Rainplots.RData")

@@

## Plot Errors and Omissions Data
# Create list and loop through plots
source('Functions/Error_RainPlots.R')
if(!file.exists("Output/Errors_Rainplots.RData")){
Error_comp_xvals <- "Accuracy"
Error_comp_groupvals <- c("Target","CueType","Distractor")
